Topic modeling on EU and the USA research projects

### 2017-06-18 thesis_report/draft_thesis.tex
Update: Topic evolution in USA

>>>>

In figure X we plot the topic distribition over time. We can easily observe that
the topic 6, which refers to STEM education, is becoming a trend in the United
States over the years, while most of the other topics' evolution doesn't show up
such a high increace. Topics 5 and 8, which refer to Chemistry \& Materials
science and Molecular biology, respectively, show a small decreace over the
years.  +++

In general, the STEM (science, technology, engineering and math) related
research and education is becoming more and more popular, which is not
surprising, since the National Science Foundation itself estimates that 80/% of
the jobs available during the next decade will require math and science skills.
Even the concept of STEM was first introduced by Judith A. Ramaley, the former
director of the National Science Foundation’s education and human resources
division.
